Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-09-25 analysis/paper/sim_survey_paper.Rmd
Tweak intro, add assumptions section and start discussion

Two main approaches have been applied to try and answer this question: one involves statistical estimators of effective sample size [@Pennington2002; @Stewart2014], and the other employs resampling methods to test alternate sampling protocol [@Cervino2006; @Zhang2013]. Both approaches have shown that lengths are usually oversampled and a reduction in said sampling can often be done without significant loss of accuracy [@Pennington2002]. The same result holds for other positively correlated characteristics, such as age [@Coggins2013] and stomach contents [@Bogstad1995]. Pennington and Vølstad [-@Pennington1994] concluded that the best way to improve the accuracy of surveys with strong intra-haul correlation is to take fewer samples per sampling unit and increase the total number of sampling locations. Few studies, however, have tested these conclusions using simulations. A key advantage of a pure simulation approach is that "true" population size and all stages of sampling can be controlled (set, length and age sampling protocol). The relative effects of each stage of sampling on our perception of the "truth" can then be tested. This level of testing is of particular importance for age composition estimates, and the contemporary age-based assessment models that rely on these estimates, as they are affected by all stages of sampling. A key challenge, of course, is building a simulation that emulates reality.

@@

@@

@@

- Look into the ictopelagic sampling design literature (suggestion from Pierre)
- Mention that simulation is an approach widely applied to inform sampling design (program MARK, distance, RandomForest, etc.); i.e. cite the gods
- Look into work done on occupancy modeling and sampling design for such studies (i.e. book suggestion by Aaron)

>>>>

Two main approaches have been applied to try and answer this question: one involves statistical estimators of effective sample size [@Pennington2002; @Stewart2014], and the other employs resampling methods to test alternate sampling protocol [@Cervino2006; @Zhang2013]. Both approaches have shown that lengths are usually oversampled and a reduction in said sampling can often be done without significant loss of accuracy [@Pennington2002]. The same result holds for other positively correlated characteristics, such as age [@Coggins2013] and stomach contents [@Bogstad1995]. Pennington and Vølstad [-@Pennington1994] concluded that the best way to improve the accuracy of surveys with strong intra-haul correlation is to take fewer samples per sampling unit and increase the total number of sampling locations. Few studies, however, have tested these conclusions using simulations. Simulations are a useful approach for informing the design of surveys [@sutherland2006] and they have been used widely for exploring the number of samples needed to obtain estimates with reasonable precision [e.g. distance sampling surveys; @thomas2010]. A key advantage of a pure simulation approach is that "true" population size and all stages of sampling can be controlled (set, length and age sampling protocol). The relative effects of each stage of sampling on our perception of the "truth" can then be tested. This level of testing is of particular importance for age composition estimates, and the contemporary age-based assessment models that rely on these estimates, as they are affected by all stages of sampling. A key challenge, of course, is building a simulation that emulates reality.

@@

## Assumptions

Like any model, this simulation is a simplification of a much more complex reality. For instance, the population is assumed to be uniformly distributed within a cell when, in the real-world, there are likely finer-scale aggregations. The survey is also an instantaneous snapshot of the population, meaning that the population is assumed to be in the same location from the beginning to the end of the survey. Also, fish are aged at random within length bins and ages are estimated without error. Finally, area trawled is assumed to be perfectly standard. This is a short, non-inclusive, list of additional variability that likely occurs in the real-world but was not implemented here for simplicity.

@@

The simple simulation presented here revealed some expected and unexpected patterns. First, there were clear improvements to precision in all population estimates as the number of sets were increased. This result was expected as it aligns with a basic principle of survey design that the precision and representativeness of a survey is increased by increasing the number of sampling units [@sutherland2006].

@@

- Look into the ictopelagic sampling design literature (suggestion from Pierre)
- Look into work done on occupancy modeling and sampling design for such studies (i.e. book suggestion by Aaron)
